Approximation as Differentiation

### 2025-03-31 notes/sec/cmon-enriched.tex
secrefs.
C -> D.
Rename.
Or coproducts.
copair-ε.

\subsection{$\CMon$-enriched categories}

@@

$\CMon$ is symmetric closed monoidal, with the trivial one-element monoid $\One$ as terminal object, monoidal
product $A \tensor B$ given by the direct product of $A$ and $B$, and braiding given by the isomorphism $A
\times B \iso B \times A$. $\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.

@@

$\CMon$ is closed monoidal, and so enriched over itself. Thus every hom-object $\CMon(A,B)$ is a commutative
monoid of commutative monoid homomorphisms where:
\begin{enumerate}
\item the unit $0$ is the constant homomorphism sending every element of $A$ to $\varepsilon_B$;
\item addition of morphisms $+$ is defined pointwise so that $(f + g)(a) = f(a) + g(a)$.
\end{enumerate}

>>>>

\subsection{$\CMon$-enriched categories}
\label{sec:cmon-enriched}

@@

$\CMon$ is symmetric closed monoidal, with the trivial one-element monoid $\One$ as terminal object, monoidal
product $A \tensor B$ given by the Cartesian product of $A$ and $B$, and braiding given by the isomorphism $A
\times B \iso B \times A$. $\CMon$ is complete and cocomplete, inheriting all limits and colimits from $\Set$.

@@

$\CMon$ is closed monoidal, and so enriched over itself. More specifically every hom-object $\CMon(A,B)$ is a
commutative monoid of commutative monoid homomorphisms where:

\begin{enumerate}
\item the unit $0$ is the constant homomorphism sending every element of $A$ to $\varepsilon_B$;
\item addition of morphisms $+$ is defined pointwise so that $(f + g)(a) = f(a) + g(a)$.
\end{enumerate}
